---
title: "Dynamic models incl. ABM using EpiModel"
author: "Kushan De Silva"
date: "May 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Three classes of models can be constructed in EpiModel; Deterministic Compartmental Models, Stochastic Individual Contact Models, Stochastic Network Models (ERGM)

Three infectious disease types can be run across all of the three classes above; Susceptible-Infectious (SI) (e.g. HIV), Susceptible-Infectious-Recovered (SIR), Susceptible-Infectious-Susceptible (SIS) (e.g. STI such as Ghonorrhea)

```{r}
library(EpiModel)
## A One-group SIS model with varying act.rate
param <- param.dcm(inf.prob = 0.2, act.rate = seq(0.05, 0.5, 0.05),
rec.rate = 1/50)
init <- init.dcm(s.num = 500, i.num = 1)
control <- control.dcm(type = "SIS", nsteps = 500)
mod1 <- dcm(param, init, control)
head(as.data.frame(mod1, run = 1))
head(as.data.frame(mod1, run = 10))

##Two-group SIR model with vital dynamics
param <- param.dcm(inf.prob = 0.2, inf.prob.g2 = 0.1,
act.rate = 3, balance = "g1",
rec.rate = 1/50, rec.rate.g2 = 1/50,
b.rate = 1/100, b.rate.g2 = NA,
ds.rate = 1/100, ds.rate.g2 = 1/100,
di.rate = 1/90, di.rate.g2 = 1/90,
dr.rate = 1/100, dr.rate.g2 = 1/100)
init <- init.dcm(s.num = 500, i.num = 1, r.num = 0,
s.num.g2 = 500, i.num.g2 = 1, r.num.g2 = 0)
control <- control.dcm(type = "SIR", nsteps = 500)
mod2 <- dcm(param, init, control)
head(as.data.frame(mod2))
tail(as.data.frame(mod2))

## Stochastic ICM SIS model with 5 simulations
param <- param.icm(inf.prob = 0.8, act.rate = 2, rec.rate = 0.1)
init <- init.icm(s.num = 500, i.num = 1)
control <- control.icm(type = "SIS", nsteps = 25,
nsims = 2, verbose = FALSE)
mod <- icm(param, init, control)
# Default output is mean across simulations
as.data.frame(mod)
# Standard deviations of simulations
as.data.frame(mod, out = "sd")
# Quantile values for interquartile interval
as.data.frame(mod, out = "qnt", qval = 0.25)
as.data.frame(mod, out = "qnt", qval = 0.75)
# Individual simulation runs, with default sim="all"
as.data.frame(mod, out = "vals")
as.data.frame(mod, out = "vals", sim = 2)
## Stochastic SI network model
nw <- network.initialize(n = 100, directed = FALSE)
formation <- ~edges
target.stats <- 50
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 20)
est <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
param <- param.net(inf.prob = 0.5)
init <- init.net(i.num = 10)
control <- control.net(type = "SI", nsteps = 10, nsims = 2, verbose = FALSE)
mod <- netsim(est, param, init, control)
as.data.frame(mod)
as.data.frame(mod, out = "vals")

set.seed(10)
nw <- network.initialize(n = 100, directed = FALSE)
formation <- ~edges
target.stats <- 50
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 20)
est1 <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
param <- param.net(inf.prob = 0.5)
init <- init.net(i.num = 1)
control <- control.net(type = "SI", nsteps = 40, nsims = 1, verbose = FALSE,
use.pids = FALSE)
mod1 <- netsim(est1, param, init, control)
tm <- get_transmat(mod1)
tmPhylo <- as.phylo.transmat(tm)
plot(tmPhylo, show.node.label = TRUE,
root.edge = TRUE,
cex = 0.5)

# Calculate equilibrium for a DCM
param <- param.dcm(inf.prob = 0.2, inf.prob.g2 = 0.1, act.rate = 0.5,
balance = "g1", rec.rate = 1 / 50, rec.rate.g2 = 1 / 50,
b.rate = 1 / 100, b.rate.g2 = NA, ds.rate = 1 / 100,
ds.rate.g2 = 1 / 100, di.rate = 1 / 90,
di.rate.g2 = 1 / 90)
init <- init.dcm(s.num = 500, i.num = 1,
s.num.g2 = 500, i.num.g2 = 1)
control <- control.dcm(type = "SIS", nsteps = 500, verbose = FALSE)
x <- dcm(param, init, control)
plot(x)
# Different calculation options
calc_eql(x, nsteps = 100)
calc_eql(x, nsteps = 250)
calc_eql(x, nsteps = 100, numer = "i.num.g2", denom = "num.g2")
calc_eql(x, nsteps = 100, numer = "i.num.g2", denom = "num.g2",
threshold = 0.00001)

# An imbalanced distribution
check_bip_degdist(num.m1 = 500, num.m2 = 500,
deg.dist.m2 = c(0.40, 0.55, 0.03, 0.02),
deg.dist.m1 = c(0.48, 0.41, 0.08, 0.03))
# A balanced distribution
check_bip_degdist(num.m1 = 500, num.m2 = 500,
deg.dist.m1 = c(0.40, 0.55, 0.04, 0.01),
deg.dist.m2 = c(0.48, 0.41, 0.08, 0.03))

##DCM SIR model with varying act.rate
param <- param.dcm(inf.prob = 0.2, act.rate = 5:7,
rec.rate = 1/3, b.rate = 1/90, ds.rate = 1/100,
di.rate = 1/35, dr.rate = 1/100)
init <- init.dcm(s.num = 1000, i.num = 1, r.num = 0)
control <- control.dcm(type = "SIR", nsteps = 25, verbose = FALSE)
mod1 <- dcm(param, init, control)
comp_plot(mod1, at = 25, run = 3)
##ICM SIR model with 3 simulations
param <- param.icm(inf.prob = 0.2, act.rate = 3, rec.rate = 1/50,
b.rate = 1/100, ds.rate = 1/100,
di.rate = 1/90, dr.rate = 1/100)
init <- init.icm(s.num = 500, i.num = 1, r.num = 0)
control <- control.icm(type = "SIR", nsteps = 25,
nsims = 3, verbose = FALSE)
mod2 <- icm(param, init, control)
comp_plot(mod2, at = 25, digits = 1)

##SI Model (One-Group)
# Set parameters
param <- param.dcm(inf.prob = 0.2, act.rate = 0.25)
init <- init.dcm(s.num = 500, i.num = 1)
control <- control.dcm(type = "SI", nsteps = 500)
mod1 <- dcm(param, init, control)
mod1
plot(mod1)
##SIR Model with Vital Dynamics (One-Group)
param <- param.dcm(inf.prob = 0.2, act.rate = 5,
rec.rate = 1/3, b.rate = 1/90, ds.rate = 1/100,
di.rate = 1/35, dr.rate = 1/100)
init <- init.dcm(s.num = 500, i.num = 1, r.num = 0)
control <- control.dcm(type = "SIR", nsteps = 500)
mod2 <- dcm(param, init, control)
mod2
plot(mod2)
##SIS Model with act.rate Sensitivity Parameter
param <- param.dcm(inf.prob = 0.2, act.rate = seq(0.1, 0.5, 0.1),
rec.rate = 1/50)
init <- init.dcm(s.num = 500, i.num = 1)
control <- control.dcm(type = "SIS", nsteps = 500)
mod3 <- dcm(param, init, control)
mod3
plot(mod3)
##SI Model with Vital Dynamics (Two-Group)
param <- param.dcm(inf.prob = 0.4, inf.prob.g2 = 0.1,
act.rate = 0.25, balance = "g1",
b.rate = 1/100, b.rate.g2 = NA,
ds.rate = 1/100, ds.rate.g2 = 1/100,
di.rate = 1/50, di.rate.g2 = 1/50)
init <- init.dcm(s.num = 500, i.num = 1,
s.num.g2 = 500, i.num.g2 = 0)
control <- control.dcm(type = "SI", nsteps = 500)
mod4 <- dcm(param, init, control)
mod4
plot(mod4)


# Homogeneous dissolution model with no deaths
dissolution_coefs(dissolution = ~offset(edges), duration = 25)
# Homogeneous dissolution model with deaths
dissolution_coefs(dissolution = ~offset(edges), duration = 25,
d.rate = 0.001)
# Heterogeneous dissolution model in which same-race edges have
# shorter duration compared to mixed-race edges, with no deaths
dissolution_coefs(dissolution = ~offset(edges) + offset(nodematch("race")),
duration = c(20, 10))
# Heterogeneous dissolution model in which same-race edges have
# shorter duration compared to mixed-race edges, with deaths
dissolution_coefs(dissolution = ~offset(edges) + offset(nodematch("race")),
duration = c(20, 10), d.rate = 0.001)

# Initialize and parameterize network model
nw <- network.initialize(n = 100, directed = FALSE)
formation <- ~edges
target.stats <- 50
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 20)
# Model estimation
est <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
# Simulate the network and extract a timed edgelist
sim <- netdx(est, nsims = 1, nsteps = 100, verbose = FALSE)
el <- sim$edgelist[[1]]
# Calculate censoring
edgelist_censor(el)

## Deterministic compartmental models
epiweb(class = "dcm")
## Stochastic individual contact models
epiweb(class = "icm")
## Stochastic network models
epiweb(class = "net")

param <- param.icm(inf.prob = 0.2, act.rate = 0.25)
init <- init.icm(s.num = 500, i.num = 1)
control <- control.icm(type = "SI", nsteps = 250, nsims = 5)
mod1 <- icm(param, init, control)
df <- as.data.frame(mod1, out = "vals")
df.mean <- as.data.frame(mod1)
library(ggplot2)
ggplot() +
geom_line(data = df, mapping = aes(time, i.num, group = sim), alpha = 0.25,
lwd = 0.25, color = "firebrick") +
geom_bands(data = df, mapping = aes(time, i.num),
lower = 0.1, upper = 0.9, fill = "firebrick") +
geom_line(data = df.mean, mapping = aes(time, i.num)) +
theme_minimal()

nw <- network.initialize(500, directed = FALSE)
set.seed(1)
fit <- ergm(nw ~ edges, target.stats = 250)
sim <- simulate(fit)
# Slow ERGM-based method
ergm.method <- unname(summary(sim ~ sociality(base = 0)))
ergm.method
# Fast tabulate method with network object
deg.net <- get_degree(sim)
deg.net
# Even faster if network already transformed into an edgelist
el <- as.edgelist(sim)
deg.el <- get_degree(el)
deg.el
identical(ergm.method, deg.net, deg.el)

## Simulate SI epidemic on bipartite Bernoulli random graph
nw <- network.initialize(n = 100, bipartite = 50, directed = FALSE)
formation <- ~edges
target.stats <- 50
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 20)
est <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
param <- param.net(inf.prob = 0.3, inf.prob.m2 = 0.15)
init <- init.net(i.num = 10, i.num.m2 = 10)
control <- control.net(type = "SI", nsteps = 10, nsims = 3, verbose = FALSE)
mod <- netsim(est, param, init, control)
## Extract the network from simulation 2
get_network(mod, sim = 2)
## Extract and collapse the network from simulation 1
get_network(mod, collapse = TRUE, at = 5)


## Simulate SI epidemic on bipartite Bernoulli random graph
nw <- network.initialize(n = 100, bipartite = 50, directed = FALSE)
formation <- ~edges
target.stats <- 50
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 20)
est <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
param <- param.net(inf.prob = 0.3, inf.prob.m2 = 0.15)
init <- init.net(i.num = 10, i.num.m2 = 10)
control <- control.net(type = "SI", nsteps = 10, nsims = 3,
nwstats.formula = ~edges + meandeg + degree(0:5),
verbose = FALSE)
mod <- netsim(est, param, init, control)
## Extract the network statistics from simulation 2
get_nwstats(mod)
get_nwstats(mod, sim = c(1,3))

#SI Model
param <- param.icm(inf.prob = 0.2, act.rate = 0.25)
init <- init.icm(s.num = 500, i.num = 1)
control <- control.icm(type = "SI", nsteps = 500, nsims = 10)
mod1 <- icm(param, init, control)
mod1
plot(mod1)

#SIR Model
param <- param.icm(inf.prob = 0.2, act.rate = 0.25, rec.rate = 1/50)
init <- init.icm(s.num = 500, i.num = 1, r.num = 0)
control <- control.icm(type = "SIR", nsteps = 500, nsims = 10)
mod2 <- icm(param, init, control)
mod2
plot(mod2)
#SIS Model
param <- param.icm(inf.prob = 0.2, act.rate = 0.25, rec.rate = 1/50)
init <- init.icm(s.num = 500, i.num = 1)
control <- control.icm(type = "SIS", nsteps = 500, nsims = 10)
mod3 <- icm(param, init, control)
mod3
plot(mod3)
#SI Model with Vital Dynamics (Two-Group)
param <- param.icm(inf.prob = 0.4, inf.prob.g2 = 0.1,
act.rate = 0.25, balance = "g1",
b.rate = 1/100, b.rate.g2 = NA,
ds.rate = 1/100, ds.rate.g2 = 1/100,
di.rate = 1/50, di.rate.g2 = 1/50)
init <- init.icm(s.num = 500, i.num = 1,
s.num.g2 = 500, i.num.g2 = 0)
control <- control.icm(type = "SI", nsteps = 500, nsims = 10)
mod4 <- icm(param, init, control)
mod4
plot(mod4)

#using status.vector and infTime.vector together
n <- 100
status <- sample(c("s", "i"), size = n, replace = TRUE, prob = c(0.8, 0.2))
infTime <- rep(NA, n)
infTime[which(status == "i")] <- -rgeom(sum(status == "i"), prob = 0.01) + 2
init.net(status.vector = status, infTime.vector = infTime)

## Simulate SI epidemic on bipartite Bernoulli random graph
nw <- network.initialize(n = 100, bipartite = 50, directed = FALSE)
formation <- ~edges
target.stats <- 50
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 20)
est <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
param <- param.net(inf.prob = 0.3, inf.prob.m2 = 0.15)
init <- init.net(i.num = 10, i.num.m2 = 10)
control <- control.net(type = "SI", nsteps = 10, nsims = 3, verbose = FALSE)
mod <- netsim(est, param, init, control)
## Extract the transmission matrix from simulation 2
get_transmat(mod, sim = 2)

param <- param.icm(inf.prob = 0.2, act.rate = 0.8)
init <- init.icm(s.num = 1000, i.num = 100)
control <- control.icm(type = "SI", nsteps = 10,
nsims = 3, verbose = FALSE)
x <- icm(param, init, control)
control <- control.icm(type = "SI", nsteps = 10,
nsims = 1, verbose = FALSE)
y <- icm(param, init, control)
z <- merge(x, y)
x$epi
y$epi
z$epi

# Network model
nw <- network.initialize(n = 100, directed = FALSE)
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 10)
est <- netest(nw, formation = ~edges, target.stats = 25,
coef.diss = coef.diss, verbose = FALSE)
# Epidemic models
param <- param.net(inf.prob = 1)
init <- init.net(i.num = 1)
control <- control.net(type = "SI", nsteps = 20, nsims = 2,
save.nwstats = TRUE,
nwstats.formula = ~edges + degree(0),
verbose = FALSE)
x <- netsim(est, param, init, control)
y <- netsim(est, param, init, control)
# Merging
z <- merge(x, y)
x$epi
y$epi
z$epi

# DCM example
param <- param.dcm(inf.prob = 0.2, act.rate = 0.25)
init <- init.dcm(s.num = 500, i.num = 1)
control <- control.dcm(type = "SI", nsteps = 500)
mod1 <- dcm(param, init, control)
mod1 <- mutate_epi(mod1, prev = i.num/num)
plot(mod1, y = "prev")
# Network model example
nw <- network.initialize(n = 100, bipartite = 50, directed = FALSE)
formation <- ~edges
target.stats <- 50
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 20)
est1 <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
# Epidemic model
param <- param.net(inf.prob = 0.3, inf.prob.m2 = 0.15)
init <- init.net(i.num = 1, i.num.m2 = 0)
control <- control.net(type = "SI", nsteps = 10, nsims = 3,
verbose = FALSE)
mod1 <- netsim(est1, param, init, control)
mod1
# Add the prevalences to the dataset
mod1 <- mutate_epi(mod1, i.prev = i.num / num,
i.prev.m2 = i.num.m2 / num.m2)
plot(mod1, y = c("i.prev", "i.prev.m2"), qnts = 0.5, legend = TRUE)
# Add incidence rate per 100 person years (assume time step = 1 week)
mod1 <- mutate_epi(mod1, ir100 = 5200*(si.flow + si.flow.m2) /(s.num + s.num.m2))
df <- as.data.frame(mod1)

# Network initialization and model parameterization
nw <- network.initialize(100, directed = FALSE)
formation <- ~edges
target.stats <- 50
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 25)
# Estimate the model
est <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
# Static diagnostics on the ERGM fit
dx1 <- netdx(est, nsims = 1e4, dynamic = FALSE,
nwstats.formula = ~edges + meandeg + concurrent)
dx1
plot(dx1, method = "b", stats = c("edges", "concurrent"))
# Dynamic diagnostics on the STERGM approximation
dx2 <- netdx(est, nsims = 5, nsteps = 500,
nwstats.formula = ~edges + meandeg + concurrent,
set.control.ergm = control.simulate.ergm(MCMC.burnin = 1e6))
dx2
plot(dx2, stats = c("edges", "meandeg"), plots.joined = FALSE)
plot(dx2, type = "duration")
plot(dx2, type = "dissolution", qnts.col = "orange2")
plot(dx2, type = "dissolution", method = "b", col = "bisque")

# Initialize a network of 100 nodes
nw <- network.initialize(n = 100, directed = FALSE)
# Set formation formula
formation <- ~edges + concurrent
# Set target statistics for formation
target.stats <- c(50, 25)
# Obtain the offset coefficients
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 10)
# Estimate the STERGM using the edges dissolution approximation
est <- netest(nw, formation, target.stats, coef.diss,
set.control.ergm = control.ergm(MCMC.burnin = 1e5,
MCMC.interval = 1000))
est
# To estimate the STERGM directly, use edapprox = FALSE
est2 <- netest(nw, formation, target.stats, coef.diss, edapprox = FALSE)
est2


##Independent SI Model
# Network model estimation
nw <- network.initialize(n = 100, bipartite = 50, directed = FALSE)
formation <- ~edges
target.stats <- 50
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 20)
est1 <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
# Epidemic model
param <- param.net(inf.prob = 0.3, inf.prob.m2 = 0.15)
init <- init.net(i.num = 10, i.num.m2 = 10)
control <- control.net(type = "SI", nsteps = 100, nsims = 5, verbose.int = 0)
mod1 <- netsim(est1, param, init, control)
# Print, plot, and summarize the results
mod1
plot(mod1)
summary(mod1, at = 50)
##Dependent SIR Model
# Recalculate dissolution coefficient with death rate
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 20,
d.rate = 0.0021)
# Reestimate the model with new coefficient
est2 <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
# Reset parameters to include demographic rates
param <- param.net(inf.prob = 0.3, inf.prob.m2 = 0.15,
rec.rate = 0.02, rec.rate.m2 = 0.02,
b.rate = 0.002, b.rate.m2 = NA,
ds.rate = 0.001, ds.rate.m2 = 0.001,
di.rate = 0.001, di.rate.m2 = 0.001,
dr.rate = 0.001, dr.rate.m2 = 0.001)
init <- init.net(i.num = 10, i.num.m2 = 10,
r.num = 0, r.num.m2 = 0)
control <- control.net(type = "SIR", nsteps = 100, nsims = 5)
# Simulate the model with new network fit
mod2 <- netsim(est2, param, init, control)
# Print, plot, and summarize the results
mod2
plot(mod2)
summary(mod2, at = 100)

# Deterministic SIR model with varying act rate
param <- param.dcm(inf.prob = 0.2, act.rate = 1:10,
rec.rate = 1/3, b.rate = 0.011, ds.rate = 0.01,
di.rate = 0.03, dr.rate = 0.01)
init <- init.dcm(s.num = 1000, i.num = 1, r.num = 0)
control <- control.dcm(type = "SIR", nsteps = 100, dt = 0.25)
mod <- dcm(param, init, control)
# Plot disease prevalence by default
plot(mod)
# Plot prevalence of susceptibles
plot(mod, y = "s.num", popfrac = TRUE, col = "Greys")
# Plot number of susceptibles
plot(mod, y = "s.num", popfrac = FALSE, col = "Greys", grid = TRUE)
# Plot multiple runs of multiple compartments together
plot(mod, y = c("s.num", "i.num"),run = 5, xlim = c(0, 50), grid = TRUE)
plot(mod, y = c("s.num", "i.num"),
run = 10, lty = 2, legend = "n", add = TRUE)

## Plotting multiple compartment values from SIR model
param <- param.icm(inf.prob = 0.5, act.rate = 0.5, rec.rate = 0.02)
init <- init.icm(s.num = 500, i.num = 1, r.num = 0)
control <- control.icm(type = "SIR", nsteps = 100,
nsims = 3, verbose = FALSE)
mod <- icm(param, init, control)
plot(mod, grid = TRUE)
## Plot only infected with specific output from SI model
param <- param.icm(inf.prob = 0.25, act.rate = 0.25)
init <- init.icm(s.num = 500, i.num = 10)
control <- control.icm(type = "SI", nsteps = 100,
nsims = 3, verbose = FALSE)
mod2 <- icm(param, init, control)
# Plot prevalence
plot(mod2, y = "i.num", mean.line = FALSE, sim.lines = TRUE)
# Plot incidence
par(mfrow = c(1, 2))
plot(mod2, y = "si.flow", mean.smooth = TRUE, grid = TRUE)
plot(mod2, y = "si.flow", qnts.smooth = FALSE, qnts = 1)


# Network initialization and model parameterization
nw <- network.initialize(100, directed = FALSE)
nw <- set.vertex.attribute(nw, "sex", rbinom(100, 1, 0.5))
formation <- ~edges + nodematch("sex")
target.stats <- c(50, 40)
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 50)
# Estimate the model
est <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
# Static diagnostics
dx1 <- netdx(est, nsims = 1e4, dynamic = FALSE,
nwstats.formula = ~edges + meandeg + concurrent +
nodefactor("sex", base = 0) +
nodematch("sex"))
dx1
# Only formation diagnostics are available to plot
plot(dx1, stats = "edges")
plot(dx1, stats = c("edges", "concurrent"))
plot(dx1, stats = "edges", method = "b", col = "seagreen3", grid = TRUE)
plot(dx1, stats = c("nodefactor.sex.0", "nodefactor.sex.1"),
method = "b", col = transco(2:3, 0.5))
# Dynamic diagnostics
dx2 <- netdx(est, nsims = 10, nsteps = 500,
nwstats.formula = ~edges + meandeg + concurrent +
nodefactor("sex", base = 0) +
nodematch("sex"))
dx2
# Formation statistics plots, joined and separate
plot(dx2, grid = TRUE)
plot(dx2, type = "formation", plots.joined = TRUE)
plot(dx2, type = "formation", sims = 1, plots.joined = TRUE,
qnts = FALSE, sim.lines = TRUE, mean.line = FALSE)
plot(dx2, type = "formation", plots.joined = FALSE,
stats = c("edges", "concurrent"), grid = TRUE)
plot(dx2, type = "formation", stats = "nodefactor.sex.0",
sims = 1, sim.lwd = 5, sim.col = "darkmagenta")
plot(dx2, method = "b", col = "bisque", grid = TRUE)
plot(dx2, method = "b", stats = "meandeg", col = "dodgerblue")
# Duration statistics plot
plot(dx2, type = "duration", mean.col = "black", grid = TRUE)
plot(dx2, type = "duration", sims = 10, mean.line = FALSE, sim.line = TRUE,
sim.col = "steelblue", sim.lwd = 3, targ.lty = 1, targ.lwd = 0.5)
# Dissolution statistics plot
plot(dx2, type = "dissolution", mean.col = "black", grid = TRUE)
plot(dx2, type = "dissolution", method = "b", col = "pink1")



## Independent SI Model
# Initialize network and set network model parameters
nw <- network.initialize(n = 100, bipartite = 50, directed = FALSE)
formation <- ~edges
target.stats <- 50
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 20)
# Estimate the network model
est <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
# Simulate the epidemic model
param <- param.net(inf.prob = 0.3, inf.prob.m2 = 0.15)
init <- init.net(i.num = 10, i.num.m2 = 10)
control <- control.net(type = "SI", nsteps = 20, nsims = 3,
verbose = FALSE, save.nwstats = TRUE,
nwstats.formula = ~edges + meandeg + concurrent)
mod <- netsim(est, param, init, control)
# Plot epidemic trajectory
plot(mod)
plot(mod, type = "epi")
plot(mod, type = "epi", grid = TRUE)
plot(mod, type = "epi", popfrac = TRUE)
plot(mod, type = "epi", y = "si.flow", qnts = 1, ylim = c(0, 4))
# Plot static networks
par(mar = c(0,0,0,0))
plot(mod, type = "network")
# Automatic coloring of infected nodes as red
par(mfrow = c(1, 2), mar = c(0, 0, 2, 0))
plot(mod, type = "network", main = "Min Prev | Time 50",
col.status = TRUE, at = 20, sims = "min")
plot(mod, type = "network", main = "Max Prev | Time 50",
col.status = TRUE, at = 20, sims = "max")
# Automatic shape by mode number (circle = mode 1)
par(mar = c(0,0,0,0))
plot(mod, type = "network", at = 20, col.status = TRUE, shp.bip = "square")
plot(mod, type = "network", at = 20, col.status = TRUE, shp.bip = "triangle")
# Plot formation statistics
par(mfrow = c(1,1), mar = c(3,3,1,1), mgp = c(2,1,0))
plot(mod, type = "formation", grid = TRUE)
plot(mod, type = "formation", plots.joined = FALSE)
plot(mod, type = "formation", sims = 2:3)
plot(mod, type = "formation", plots.joined = FALSE,
stats = c("edges", "concurrent"))
plot(mod, type = "formation", stats = "meandeg",
sim.lwd = 2, sim.col = "seagreen")

## Deterministic SIR model with varying act.rate
param <- param.dcm(inf.prob = 0.2, act.rate = 2:4, rec.rate = 1/3,
b.rate = 0.011, ds.rate = 0.01,
di.rate = 0.03, dr.rate = 0.01)
init <- init.dcm(s.num = 1000, i.num = 1, r.num = 0)
control <- control.dcm(type = "SIR", nsteps = 50)
mod <- dcm(param, init, control)
summary(mod, at = 25, run = 1)
summary(mod, at = 25, run = 3)
summary(mod, at = 26, run = 3)


## Stochastic ICM SI model with 3 simulations
param <- param.icm(inf.prob = 0.2, act.rate = 1)
init <- init.icm(s.num = 500, i.num = 1)
control <- control.icm(type = "SI", nsteps = 50,
nsims = 5, verbose = FALSE)
mod <- icm(param, init, control)
summary(mod, at = 25)
summary(mod, at = 50)

## Independent SI Model
# Initialize network and set network model parameters
nw <- network.initialize(n = 100, bipartite = 50, directed = FALSE)
formation <- ~edges
target.stats <- 50
coef.diss <- dissolution_coefs(dissolution = ~offset(edges), duration = 20)
# Estimate the ERGM models (see help for netest)
# Skipping model diagnostics for this, but one should always run these
est1 <- netest(nw, formation, target.stats, coef.diss, verbose = FALSE)
# Parameters, initial conditions, and controls for model
param <- param.net(inf.prob = 0.3, inf.prob.m2 = 0.15)
init <- init.net(i.num = 10, i.num.m2 = 10)
control <- control.net(type = "SI", nsteps = 100, nsims = 5, verbose.int = 0)
# Run the model simulation
mod <- netsim(est1, param, init, control)
summary(mod, at = 1)
summary(mod, at = 50)
summary(mod, at = 100)


set.seed(12345)
param <- param.icm(inf.prob = 0.2, act.rate = 0.25)
init <- init.icm(s.num = 500, i.num = 1)
control <- control.icm(type = "SI", nsteps = 200, nsims = 1)
mod1 <- icm(param, init, control)
df <- as.data.frame(mod1, out = "vals")
print(df)
plot(mod1)
mod1$control$nsteps
mod2 <- truncate_sim(mod1, at = 150)
df2 <- as.data.frame(mod2)
print(df2)
plot(mod2)
mod2$control$nsteps


nw <- network.initialize(1000, directed = FALSE)
# Two dissolutions: an average duration of 300 versus 200
diss.300 <- dissolution_coefs(~offset(edges), 300, 0.001)
diss.200 <- dissolution_coefs(~offset(edges), 200, 0.001)
# Fit the two reference models
est300 <- netest(nw = nw,
formation = ~edges,
target.stats = c(500),
coef.diss = diss.300)
est200 <- netest(nw = nw,
formation = ~edges,
target.stats = c(500),
coef.diss = diss.200)
# Alternatively, update the 300 model with the 200 coefficients
est200.compare <- update_dissolution(est300, diss.200)
identical(est200$coef.form, est200.compare$coef.form)

```

